%-------------------------
% Resume in Latex
% Author : Tushar Pandey
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
{#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #2 \\
  \textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Tushar Pandey} \\ \vspace{4pt}
\small +919380611436 $|$ \href{mailto:tusharpandey13@gmail.com}{\underline{tusharpandey13@gmail.com}} $|$
\href{https://www.linkedin.com/in/tusharpandey13/}{\underline{linkedin.com/in/tusharpandey13}} $|$
\href{https://github.com/tusharpandey13}{\underline{github.com/tusharpandey13}}
\end{center}

%-----------PROFILE SUMMARY-----------
\section{Profile Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
\resumeItem{Full-stack Software Engineer with \textbf{4+ years} building \textbf{customer-facing products} that real businesses depend on. Shipped features end-to-end across TypeScript, React, and Node.js — from UI flows to backend pricing and policy logic. Strong ownership instinct: treats features as products, not tickets. Previously scaled services to \textbf{4,000 TPS} for \textbf{40M+ users} and maintained open-source SDKs with \textbf{21M+ monthly installs}. AI-native in daily workflow.}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Software Development Engineer 2, Authn-SDKs | Auth0 (Okta)}{July 2024 -- Present}
  {Primary maintainer of nextjs-auth0 (21M+ monthly downloads, 141\% growth in tenure)}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{\textbf{New SDK (auth0-hono)}: Owned and shipped a new full-stack authentication SDK from scratch — 8,100+ lines of code, 291 tests, running on Node, Cloudflare Workers, Deno, and Bun. Gap analysis to production in 4 weeks.}
    \resumeItem{\textbf{Multi-Factor Auth (MFA)}: Shipped end-to-end MFA step-up support — frontend challenge flows to backend factor verification and enrollment. First server-side Auth0 SDK with this capability. Design to production in 5 weeks.}
    \resumeItem{\textbf{Multi-Domain Support}: Rewired SDK from single-domain to dynamic per-request domain resolution. Zero breaking changes, sessions auto-migrate. Directly unblocked multi-brand customers.}
    \resumeItem{\textbf{Cross-SDK Features}: Delivered DPoP, token exchange, and org-scoped auth across Next.js, SPA, and Node SDKs. Cut 31 releases across 3 packages in 16 months.}
    \resumeItem{\textbf{Security}: Patched critical Next.js cache poisoning vulnerability affecting all Next.js users globally. Coordinated fix across SDK ecosystem with security team.}
    \resumeItem{\textbf{Technical Direction}: Authored 15+ design docs adopted across teams. Unblocked stalled features by shipping working prototypes over writing longer docs.}
  \resumeItemListEnd

    \resumeSubheading
  {Software Development Engineer 1, B2B-Subscriptions | ZEE5}{August 2022 -- July 2024}
  {Scaling video streaming platform for 65M+ monthly active users}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{\textbf{Subscription Engine}: Built async subscription orchestrator with automatic failover powering revenue-critical B2B flows. 99.9\% uptime, reduced cloud spend.}
    \resumeItem{\textbf{Mirage}: Built token exchange service handling 4,000 req/sec for 40M+ B2B users — the core of cross-platform entitlement and access control.}
    \resumeItem{\textbf{Cloud Migration}: Led zero-downtime AWS to GCP migration — PostgreSQL to Cloud Spanner for 5M+ daily auth events. DB latency under 10ms.}
    \resumeItem{\textbf{Platform Rewrite}: Moved Node.js services to Java WebFlux. 10x throughput, zero regressions, zero customer-facing downtime.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------KEY PROJECTS-----------
\section{Key Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{OPAL: Real-time Log Analytics (Auth0 Hackathon Finalist)} $|$ \emph{ClickHouse, S3, Benthos, Cube.js}}{}
\resumeItemListStart
  \resumeItem{Built analytics engine ingesting \textbf{13k events/sec} for customer usage insights. Estimated \textbf{\$70k/month savings} over existing solution. Live dashboards integrated into product.}
\resumeItemListEnd

\resumeProjectHeading
    {\textbf{Forge: AI Development Workflow Engine} $|$ \emph{TypeScript, Claude, State Machines}}{}
\resumeItemListStart
  \resumeItem{Multi-phase AI orchestrator automating the full software lifecycle: requirements, design, implementation, review, and documentation. Used to ship production SDK features.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, parsep=0pt]
    \resumeItem{\textbf{Languages}: TypeScript, JavaScript, Java, Python, Go}
    \resumeItem{\textbf{Frontend}: React, Next.js, Hono}
    \resumeItem{\textbf{Backend}: Node.js, Spring WebFlux, REST APIs, Vitest}
    \resumeItem{\textbf{Auth/Identity}: OAuth 2.0/2.1, OIDC, DPoP, MFA, PKCE, Token Exchange, Session Management}
    \resumeItem{\textbf{Infrastructure}: PostgreSQL, Cloud Spanner, Redis, Kafka, Cloudflare Workers, Docker, ClickHouse}
    \resumeItem{\textbf{Practices}: Full-stack ownership, design-doc-driven delivery, security review, open-source maintenance, AI-native workflow}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BMSIT, Bangalore}{}
      {Bachelor of Technology, Computer Science}{2018 -- 2022}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
