%-------------------------
% Resume in Latex
% Author : Tushar Pandey
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
{#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #2 \\
  \textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Tushar Pandey} \\ \vspace{4pt}
\small +919380611436 $|$ \href{mailto:tusharpandey13@gmail.com}{\underline{tusharpandey13@gmail.com}} $|$
\href{https://www.linkedin.com/in/tusharpandey13/}{\underline{linkedin.com/in/tusharpandey13}} $|$
\href{https://github.com/tusharpandey13}{\underline{github.com/tusharpandey13}}
\end{center}

%-----------PROFILE SUMMARY-----------
\section{Profile Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
\resumeItem{Software Engineer with \textbf{4+ years} building \textbf{identity and authentication infrastructure}. Primary maintainer of open-source SDKs with \textbf{21M+ monthly installs}. Shipped security-critical features across \textbf{11 repositories}, released \textbf{31 SDK versions}, and built a \textbf{new SDK from scratch}. Previously scaled token services to \textbf{4,000 TPS} for \textbf{40M+ users} at ZEE5.}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Software Development Engineer 2, Authn-SDKs | Auth0 (Okta)}{July 2024 -- Present}
  {Primary maintainer of nextjs-auth0 (21M+ monthly downloads, 141\% growth in tenure)}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{\textbf{Multi-Factor Auth (MFA)}: Shipped full MFA step-up support for Next.js SDK. Users can now challenge, verify, and enroll factors natively. First server-side Auth0 SDK with this capability. Design to production in 5 weeks.}
    \resumeItem{\textbf{Multi-Domain Support}: Rewired SDK from single-domain to dynamic per-request domain resolution. Customers with multiple brands now use one SDK instance. Zero breaking changes, sessions auto-migrate.}
    \resumeItem{\textbf{New SDK (auth0-hono)}: Built and shipped a new authentication SDK for the Hono framework. 8,100+ lines of code, 291 tests, runs on Node, Cloudflare Workers, Deno, and Bun. Gap analysis to shipping in 4 weeks.}
    \resumeItem{\textbf{Cross-SDK Features}: Delivered DPoP (proof-of-possession tokens), token exchange, and organization-scoped auth across Next.js, SPA, and Node SDKs. Cut 31 releases across 3 packages in 16 months.}
    \resumeItem{\textbf{Security}: Patched critical Next.js cache poisoning vulnerability (affected all Next.js users globally) across Auth0 SDK ecosystem. Owned and resolved auth parameter injection bugs and coordinated fixes with security team.}
    \resumeItem{\textbf{Technical Direction}: Authored 15+ design docs adopted across teams. Proposed and got approval for 10+ architecture decisions in cross-team reviews. Unblocked stalled features by building working prototypes instead of writing longer docs.}
  \resumeItemListEnd

    \resumeSubheading
  {Software Development Engineer 1, B2B-Subscriptions | ZEE5}{August 2022 -- July 2024}
  {Scaling video streaming platform for 65M+ monthly active users}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{\textbf{Mirage}: Built high-throughput token exchange service handling 4,000 requests/sec, powering cross-platform streaming for 40M+ B2B users (60\% of ZEE5's revenue base).}
    \resumeItem{\textbf{Cloud Migration}: Led zero-downtime AWS to GCP migration including PostgreSQL to Cloud Spanner for 5M+ daily auth events. Cut DB latency to under 10ms.}
    \resumeItem{\textbf{Subscription Engine}: Built async subscription orchestrator with automatic failover. Hit 99.9\% uptime on revenue-critical B2B flows while cutting cloud spend.}
    \resumeItem{\textbf{Platform Rewrite}: Moved Node.js services to Java WebFlux. 10x throughput, zero regressions, zero customer-facing downtime.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------KEY PROJECTS-----------
\section{Key Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{Forge: AI Development Workflow Engine} $|$ \emph{Claude Code, TypeScript, State Machines}}{}
\resumeItemListStart
  \resumeItem{Built a multi-phase AI orchestrator that automates the full software lifecycle: requirements, design, implementation, review, and documentation.}
  \resumeItem{Used to ship two major SDK features (MFA and Multi-Domain). Adopted by team for AI-assisted development.}
\resumeItemListEnd

\resumeProjectHeading
    {\textbf{OPAL: Real-time Log Analytics (Auth0 Hackathon Finalist)} $|$ \emph{ClickHouse, S3, Benthos, Cube.js}}{}
\resumeItemListStart
  \resumeItem{Built analytics engine ingesting \textbf{13k events/sec} for customer usage insights. Estimated \textbf{\$70k/month savings} over existing solution.}
  \resumeItem{Column-oriented storage with 130:1 write-read efficiency. Live dashboards and log search integrated into product.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt, parsep=0pt]
    \resumeItem{\textbf{Languages}: TypeScript, Java, Python, Go, Rust (learning)}
    \resumeItem{\textbf{Auth/Identity}: OAuth 2.0/2.1, OIDC, DPoP, MFA, PKCE, Token Exchange, Session Management}
    \resumeItem{\textbf{Frameworks}: Next.js, React, Hono, Node.js, Spring WebFlux, Vitest}
    \resumeItem{\textbf{Infrastructure}: ClickHouse, PostgreSQL, Cloud Spanner, Redis, Kafka, Cloudflare Workers, Docker}
    \resumeItem{\textbf{AI/Tooling}: Claude Code, LLM-driven automation, RAG pipelines, prompt engineering}
    \resumeItem{\textbf{Practices}: Design-doc-driven delivery, security review, release management, open-source maintenance}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BMSIT, Bangalore}{}
      {Bachelor of Technology, Computer Science}{2018 -- 2022}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
